---
title: "Task 08 Functions"
author: "Mariah Taylor"
Date: "5/2/2017"
output: md_document
---

# Function that adds WARNING messages using tryCatch
```{r}
#Open necessary packages
library (tidyverse)
library (forcats)

#Write function that follows task 08 criteria of adding "warning" messages
my_function <- function(df, x, y, z) {
  tryCatch(
    
    df[, z] <- (df[, x] + df[, y]),
           warning=function(w){
             message("Cannot sum words by a number")
             return(NA) #this is not working for some reason
             
           },
             error=function(e) {
               stop("df is not a data frame") #changed error message
             })
  return(df)
}


diamonds <- diamonds

#test function to get "warning" message
my_function(diamonds, "cut", "depth", "new.col")


#test my function to get "error" message
my_function(diamonds, "cut", "clarity", "new.col2")


#test my function to get correct dataframe column
my_function(diamonds, "depth", "table", "new.col3")
##this makes a new column labled "new.col3" that returns correct numerical values.



```

# Function that returns NA values in new column
```{r}
#Write function that follows task 08 criteria of adding non-numeric columns
add_function <- function(df, x, y, z) {
  tryCatch(df[, z] <- df[, x] + df[, y])
           warning=function(w){
             message("Cannot sum words by a number")
             return(NA)
           }
             error=function(e) {
               stop("x is not a numeric vector")
             }
  return(df)

  }
my_diamonds <- diamonds

#test my function to get "warning" message
add_function(my_diamonds, "cut", "depth", "new.col")
##this makes a new column labeled "new.col" in the diamonds dataframe that has NA values 

#test my function to get "error" message
add_function(my_diamonds, "cut", "color", "new.col2")
##this makes a new column labeled "new.col2" that has NA values.

#test my function to get correct dataframe column
add_function(my_diamonds, "depth", "table", "new.col3")
##this makes a new column labled "new.col3" that returns correct numerical values.
```
# Loop and Performance Metric Tests
## Create a function that uses a for loop to add the elements of a vector
```{r}
#For Loop: Sum of all vector elements
library(microbenchmark)
my_add <- function(x) {
  sum <- 0 
  for(i in x) {
     sum <- sum + i
  }
  return(sum)
}

```
# Compare my function to "sum" function
```{r}
#Comparing my addition function to the RStudio "sum" function
test <- 1:10^4
microbenchmark(
    my_add(test),
    sum(test)
    )

sum(1:10^4)
my_add(1:10^4)
```

# Is there a difference between the two functions? Why?
## The sum function is much more efficient than my function because it runs in a shorter time span.
